mathml: Translate R expressions to MathML and LaTeX/MathJax

### 2022-12-13 Draft3.Rmd
small changes

## Basic elements
214

215

`mathml` contains several basic elements used in everyday mathematical expressions. For example it is possible to print the function for the linear regression as:
216

217

@@

```{r, results='asis'}
f <- function(x, a)
{
    if(a == 0) return(+Inf);
    if(a == 0) return(-Inf);
    if(a > 1L ) return(frac(1L,2L))
}

@@

>>>>

## Basic elements

`mathml` contains several basic elements used in everyday mathematical expressions. 
For example it is possible to print the function for the linear regression as:

@@

_I also wanted to add a condition like 1 < a < 2, but apparently it's not possible_ 
It is also possible to represent a system of equations with different relations. Note that you may also assign a name to the function. The default name is in fact the greek letter lambda, but with `attributes()$name` the name costumization is performed smoothly.

```{r, results='asis'}
f <- function(x, a)
{
    if(a == 0L) return( 0L );
    if(a <= 1L) return(-Inf);
    if(a > 1L) return(+Inf)
}

@@

attributes(f)$name = quote(f)
mathout(f)
